Computing likelihoods under the SMC for a general class of ARGs.

### 2023-11-08 paper.tex
compile error correction

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/smc-custom-haplotypes-mini.png}
\caption{ARG (top left) generated under the SMC and its representation as a 
series of local trees. The presence of the unary nodes ensure these two 
representations contain the same information.
The haplotypes that make up the lineages coalescing 
at the root of each marginal tree are highlighted at the top. Ancestral 
material is coloured based on the samples that inherit from it.
Note how the presence of the unary nodes 
modifies the left-to-right logic of single-prune-regrafts induced by 
recombination under the SMC (blue dotted arrows).
Even in the absence of the blue recombination nodes, 
the unary coalescing nodes allow us to reconstruct the state of all lineages 
up to the exact time of the recombination event.
}
\label{fig:smc-unary}
\end{figure}

@@

\begin{figure}[h!] \label{fig:algo}
\centering
\includegraphics[width=0.8\textwidth]{figures/smc_algo.png}
\caption{Description of algorithm: the algorithm progresses from left to right and 
keeps track of the . Let's assume we have visited the first 5 edges present in the 
first tree (tabel 1). Moving onto the next tree, need to remove single edge 
$(2, 5, [0,42))$, update the counts $I$ by decrementing all intervals between 5 and 
2. The state of the vector is now $I_6$, the number of extant lineages the lineage 
associated with edge $(1, 6, [42, 100)$ can coalesce with. Now compute the likelihood 
associated with this edge. Then insert this edge and increment the count vector between 
1 and 6. Two intermediate steps to move to the second tree. Similarly again two steps 
to move to the last tree and insert edge $(5, 7, [70,100))$
}

\end{figure}

\begin{figure}[h!] \label{fig:algo-flat}
\centering
\includegraphics[width=\textwidth]{figures/ts_algo_2rows.png}
\caption{Description of algorithm: Moving along the genome we transition from the first 
local tree (1) to the next (4). For each edge that is removed from the first tree we 
decrement the count in the corresponding internode intervals and update the identity of 
the last parent. Subsequently, for each edge that will be inserted we compute the likelihood 
associated with that edge prior to incrementing the counts.}
\end{figure}

@@

\end{figure}

\begin{figure}[h!] \label{sup:fig:vs-argweaver}
\centering
\includegraphics[width=\textwidth]{example-image-a}
\caption{Compare likelihoods inferred ARGs ARGweaver}
\end{figure}

\end{figure}

\begin{figure}[h!] \label{sup:fig:vs-hudson}
\centering
\includegraphics[width=\textwidth]{example-image-a}
\caption{Compare likelihoods Hudson and SMC}
\end{figure}

>>>>

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/smc_custom_2rows.png}
\caption{ARG (top left) generated under the SMC and its representation as a 
series of local trees. The presence of the unary nodes ensure these two 
representations contain the same information.
The haplotypes that make up the lineages coalescing 
at the root of each marginal tree are highlighted at the top. Ancestral 
material is coloured based on the samples that inherit from it.
Note how the presence of the unary nodes 
modifies the left-to-right logic of single-prune-regrafts induced by 
recombination under the SMC (blue dotted arrows).
Even in the absence of the blue recombination nodes, 
the unary coalescing nodes allow us to reconstruct the state of all lineages 
up to the exact time of the recombination event.
}
\label{fig:smc-unary}
\end{figure}

@@

\begin{figure}[!ht] \label{fig:algo}
\centering
\includegraphics[width=\textwidth]{figures/ts_algo_2rows.png}
\caption{Description of algorithm: Moving along the genome we transition from the first 
local tree (1) to the next (4). For each edge that is removed from the first tree we 
decrement the count in the corresponding internode intervals and update the identity of 
the last parent. Subsequently, for each edge that will be inserted we compute the likelihood 
associated with that edge prior to incrementing the counts.}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{example-image-a}
\caption{Compare likelihoods inferred ARGs ARGweaver}
 \label{sup:fig:vs-argweaver}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{example-image-a}
\caption{Compare likelihoods Hudson and SMC}
\label{sup:fig:vs-hudson}
\end{figure}
